Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-04-21 README.rmd
updated README
misc changes

# contratrain-muscle-paper

@@

Håvard Hamarsland
<a href="https://orcid.org/0000-0002-7343-2774">
<img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a>,
Kristian Lian,
Chidimma Phoebe Echebiri,
Mads-Henrik Hafsmo,
Tomas Varpestuen,
Stein-Olaf Olsen,
Chris Sylstad,
Max Ullrich,
Stian Ellefsen
<a href="https://orcid.org/0000-0003-0467-2018">
<img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a>,
Daniel Hammarström
<a href="https://orcid.org/0000-0001-8360-2100">
<img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a>

@@

- bibliography.bib
- csl-files

@@

- contains raw data not included in the data package

`/data-gen/`

- contains generated data stored for further analyses

`contratrain-manuscript.qmd`

@@

@@

>>>>

# Ribose-paper

@@

Kristian Lian
<a href="https://orcid.org/0000-0002-5169-5960">
<img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a>,
Daniel Hammarström
<a href="https://orcid.org/0000-0001-8360-2100">
<img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> 
Stian Ellefsen
<a href="https://orcid.org/0000-0003-0467-2018">
<img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a>,
Håvard Hamarsland
<a href="https://orcid.org/0000-0002-7343-2774">
<img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a>,
Sara Christine Moen

## Abstract

@@

- Bibliography file
- Csl-files
- Reference template
- Pptx file for the blot images in figure 3
- RMD output files <!-- if you get this to work -->

@@

- Contains raw data files

`/data/data-gen/`

- Contains generated data stored for further analyses

`ribose-manuscript.rmd`

@@

`extended-methods.rmd`

- Supplementary extended methods source file

@@

`/figures/archive`

- Png and tif files of total protein stains and antibody stains

`/R`

- Scripts for data handling/cleanup and analyses

`/R/scraps`

- Old/unused scripts
